Ceph Parallel File System Evaluation Report

### 2013-08-22 abstract.tex
Did a quick breakup from original report, resize figures to fit to IEEE format.
updated the abstract

Ceph is designed to be a reliable and scalable fault tolerant parallel file
system with a number of intriguing features. In collaboration with its major
developer, Inktank Inc, we studied the feasibility of using Ceph for future
HPC storage deployment. This paper presents our experiments, results and
observations from mostly performance and scalability perspective. Our work
made two unique contributions. First, this evaluation is performed under a
realistic setup using state-of-the-art backend storage (Data Direct Network's
SFA10K),  although typical in large-scale HPC environment, but atypical for
average commercial off-the-shelf setup.  Second, our path of investigation,
tuning efforts, and findings made a direct contribution to Ceph's development,
it should also benefit community at large. Throughout the evaluation, we can
see that Ceph is under fast-paced development and maturing with great promise.

>>>>

\begin{abstract}

%Ceph is designed to be a reliable and scalable fault tolerant parallel file
%system with a number of intriguing features.

Ceph is an open-source and emerging distributed parallel file and storage
system technology. It is designed to provide file system-level and object-level
access to data. Ceph, by design, assumes running on unreliable and commodity
storage and network hardware and provides reliability and fault-tolerance
through pre-calculated and controlled object placement and data replication.

In collaboration with its major developer, Inktank Inc, we evaluated the Ceph
technology for future high-performance computing (HPC) environments, like ours.
This paper presents our evaluation methodology, experiments, results and
observations from mostly parallel I/O performance and scalability perspectives.
Our work made two unique contributions. First, our evaluation is performed
under a realistic setup for a large-scale capability HPC environment like ours
using a commercial high-end storage system (Data Direct Network's SFA10K).
%although typical in large-scale HPC environment, but atypical for average
%commercial off-the-shelf setup.  
Second, our path of investigation, tuning efforts, and findings made direct
contributions to Ceph's development and improved code quality, scalability, and
performance. These changes should also benefit the Ceph and HPC community at
large. Throughout the evaluation, we observed that Ceph still is an evloving
technology and is under fast-paced development and maturing with great promise.

\end{abstract}
